Title Goes Here

### 2020-04-10 analysis/paper/paper.Rmd
add one more plot

Computing Pearson's correlation 
```{r}
# Correlations with significance levels
# I can move the library(pkg) to the top with other libraries but I'm leaving here for my reference for a while
library(Hmisc) 
rcorr(ML, BL, type = "pearson") # type can be pearson or spearman

@@

@@

# Correlations with significance levels
library(Hmisc)
rcorr(ML,BL, type = "pearson") # type can be pearson or spearman

>>>>

@@

Computing Pearson's correlation 
```{r}
library(Hmisc)
COR <- rcorr(as.matrix(DF))

#a simple function for formatting a correlation matrix into a table with 4 columns containing from (http://www.sthda.com/english/wiki/correlation-matrix-a-quick-start-guide-to-analyze-format-and-visualize-a-correlation-matrix-using-r-software)
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

flattenCorrMatrix(COR$r, COR$P)

#simpler way to calculate Correlataion, you can use
SCOR <- cor(DF)

# Plot for SCOR
library(corrplot)
corrplot(SCOR, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

corrplot(COR$r, type="upper", order="hclust", 
         p.mat = COR$P, sig.level = 0.01, insig = "blank")
```

@@
